Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-30 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Updating the proof...

If a QIVPM\nb$\bar{\mu}$ is 0-deterministic, a family of $M$ commuting
observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ can be
diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
Since $\bar{\mu}$ is 0-deterministic, there is a quantum probability
measure\nb$\mu$ such that $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
and $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$\nb\citep{HOSTunpublished}.
Hence, the expectation values of the observables\nb$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
and the product observables\nb$\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}$
are equal to the singleton set\nb$\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} $
and $\left\{ \expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\mu}\right\} $,
respectively, which have an intuitive product rule\nb$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $.
Since $\mu\left(\proj{k}\right)$ is either $0$ or $1$, there exists
an unique $\ket{k_{0}}$ such that $\mu\left(\proj{k_{0}}\right)=1$
and $\mu\left(\proj{k}\right)=0$ for $k\ne k_{0}$, both $\prod_{j=1}^{M}\left\{ \expval{\mathbf{O}_{j}}_{\mu}\right\} $
and $\left\{ \expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\mu}\right\} $
are equal to the product of the eigenvalues corresponding to the pure
state\nb$\ket{k_{0}}$ for each observables. Therefore, we have the
following property: 
\begin{equation}
\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
\end{equation}

>>>>

If a QIVPM\nb$\bar{\mu}$ is 0-deterministic, a family of $M$ commuting
observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ can be
diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
Since $\bar{\mu}$ is 0-deterministic, there is a quantum probability
measure\nb$\mu$ such that $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
and $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$\nb\citep{HOSTunpublished}.
By denoting the product observables\nb$\prod_{j=1}^{M}\mathbf{O}_{j}$
as $\overline{\mathbf{O}}$, the expectation values of the observables\nb$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
and $\expval{\overline{\mathbf{O}}}_{\bar{\mu}}$ are equal to the
singleton sets whose only elements are $\expval{\mathbf{O}_{j}}_{\mu}$
and $\expval{\overline{\mathbf{O}}}_{\mu}$, respectively. Also, since
$\mu\left(\proj{k}\right)$ is either $0$ or $1$, there exists an
unique $\ket{k_{0}}$ such that $\mu\left(\proj{k}\right)=1$ if and
only if $k=k_{0}$. Both $\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\mu}$
and $\expval{\overline{\mathbf{O}}}_{\mu}$ are equal to the product
of the eigenvalues corresponding to the pure state\nb$\ket{k_{0}}$
for each observable\nb$\mathbf{O}_{j}$. By adopting an intuitive
product rule\nb$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $,
we have the following property: 
\begin{equation}
\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
\end{equation}
